Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-12 Latex/main.tex
Added acknowledgements
Changed author listing
acknowledgement

\begin{abstract}
Spherical robots are a format that hasn't been thoroughly explored for the application of mobile mapping. 
In contrast to other designes it provides some unique advantages. 
Among those are a protective spherical shell which protects internal sensors and actuators from possible harsh environments as well as an inherent rotation for locomotion that enables measurements in all directions.
Mobile mapping always requires a high-precise pose knowledge to obtain consistent and correct environment maps. 
This is typically be done by a combination of external reference sensors such as GNSS measurements and inertial measurements, or by post processing the data and registering the different measurements to each other. 
In indoor environments the GNSS reference is not an option, hence many mobile mapping applications turn to the second option.
An advantage of indoor environments is, that human made environments usually have a certain structure, such as parallel planes and right angles.
We propose a registration procedure that exploits this structure by minimizing the distance of measured points to a corresponding plane. 
Further we evaluate the procedure on a simulated dataset of an ideal corridor as well as in experimentally acquired datasets with different motion profiles. 
We show that we nearly reproduce the ground truth for the simulated dataset and improve the average point-to-point distance to a reference scan in the experimental dataset.
The presented algorithms are required to work completely autonomous.
\end{abstract}

@@

\input{sections/introduction}
\input{sections/stateOfTheArt}
\input{sections/registration}
\input{sections/simulation}
\input{sections/realData}
\input{sections/results}
\input{sections/conclusion}

>>>>

\begin{abstract}
Spherical robots are a format that has not been thoroughly explored for the application of mobile mapping. 
In contrast to other designes it provides some unique advantages. 
Among those are a protective spherical shell which protects internal sensors and actuators from possible harsh environments as well as an inherent rotation for locomotion that enables measurements in all directions.
Mobile mapping always requires a high-precise pose knowledge to obtain consistent and correct environment maps. 
This is typically done by a combination of external reference sensors such as Global Navigation Satellite System (GNSS) measurements and inertial measurements, or by post processing the data and registering the different measurements to each other. 
In indoor environments the GNSS reference is not an option, hence many mobile mapping applications turn to the second option.
An advantage of indoor environments is, that human made environments usually have a certain structure, such as parallel and perpendicular planes.
We propose a registration procedure that exploits this structure by minimizing the distance of measured points to a corresponding plane. 
Further we evaluate the procedure on a simulated dataset of an ideal corridor as well as in experimentally acquired datasets with different motion profiles. 
We show that we nearly reproduce the ground truth for the simulated dataset and improve the average point-to-point distance to a reference scan in the experimental dataset.
The presented algorithms are required to work completely autonomous.
\end{abstract}

@@

\input{sections/introduction}
\input{sections/stateOfTheArt}
\input{sections/registration}
\input{sections/simulation}
\input{sections/realData}
\input{sections/results}
\input{sections/conclusion}
\input{sections/acknowledgement}

### 2021-05-12 Latex/sections/acknowledgement.tex
acknowledgement

%!TEX root = ../main.tex
\section*{Acknowledgement}
\todo[inline]{Formulate these: ESA funding (?), elite netzwerk bayern (?), cylon floatsat group}

>>>>

%!TEX root = ../main.tex
\section*{Acknowledgement}
\todo[inline]{check this}
The authors thank the Cylon team (Ignacio Dorado Llamas, Timothy Randolph, Camilo Andres Reyes Mantilla, Tobias Wahl) for designing and building the prototype and Timo Burger for acquiring the floating table data set.
Special thanks to Dieter Ziegler and Sergio Montenegro for supporting our work.
We acknowledge funding from the ESA Contract No. 4000130925/20/NL/GLC for the ``DAEDALUS -- Descent And Exploration in Deep Autonomy of Lava Underground Structures'' Open Space Innovation Platform (OSIP) lunar caves-system study and the Elite Network Bavaria (ENB) for providing funds for the academic program ``Satellite Technology''.

### 2021-05-12 Latex/sections/introduction.tex
acknowledgement

Today's robots for mobile mapping come in all shapes and sizes.
The state of the art for urban environments are laser scanners mounted to cars.
Smaller robotic systems are particularly used when cars no longer have access.
Examples for this are human operated systems such as Zebedee~\cite{FIXME}, a Hokuyo scanner on a spring, VILMA~\cite{JPRS2016}, a rolling FARO scanner, RADLER~\cite{Borrmann2020-RADLER}, a 2D laser scanner mounted to a unicycle, or a backpack mounted ``personal laser scanning system'' as in~\cite{LauterbackEtAl2015-Backpack}.
Recently more and more autonomous systems gained maturity.
A stunning example is Boston Dynamics' quadruped ``Spot'' that autonomously navigates and maps human environments~\cite{SpotRobot}.
Also the mobile mapping approaches implemented on the ANYmal platform such as~\cite{Fankhauser2018-ANYmal} were very successful.
Of all these formats, one hasn't been explored thoroughly in the scientific community: The spherical mobile mapping robot.
Yet this provides some very promising advantages over the other formats.
For one, the locomotion of a spherical robot inherently results in a rotation.
That way a sensor fixed inside the spherical structure will cover the entire environment, given the required locomotion without the need for additional actuators for the sensors.
This requires a solution for the spherical simultaneous localization and mapping (SLAM) problem given the six degrees of freedom of the robot.
Secondly a spherical shell, that encloses all sensors protects these from possible hazardous environments.
For example, any dust that deteriorates sensors or actuators when settling at sensitive locations is stopped by a shell.
This is be particularly useful for unknown and dangerous environments.
E.g., for space applications this is also proposed in the DAEDALUS study~\cite{RossiMaurelliUnnithanetal.2021}, a spherical robot that is to be lowered into a lunar cave and create a 3D map of the environment. The authors choose this format as the present moon regolith is known to damage instruments and other components.

>>>>

Today's robots for mobile mapping come in all shapes and sizes.
The state of the art for urban environments are laser scanners mounted to cars.
Smaller robotic systems are particularly used when cars no longer have access.
Examples for this are human operated systems such as Zebedee~\cite{bosse2012zebedee}, a Hokuyo scanner on a spring, VILMA~\cite{JPRS2016}, a rolling FARO scanner, RADLER~\cite{Borrmann2020-RADLER}, a 2D laser scanner mounted to a unicycle, or a backpack mounted ``personal laser scanning system'' as in~\cite{LauterbackEtAl2015-Backpack}.
Recently more and more autonomous systems gained maturity.
A stunning example is Boston Dynamics' quadruped ``Spot'' that autonomously navigates and maps human environments~\cite{SpotRobot}.
Also the mobile mapping approaches implemented on the ANYmal platform such as~\cite{Fankhauser2018-ANYmal} were very successful.
Of all these formats, one hasn't been explored thoroughly in the scientific community: The spherical mobile mapping robot.
Yet this provides some very promising advantages over the other formats.
For one, the locomotion of a spherical robot inherently results in a rotation.
That way a sensor fixed inside the spherical structure will cover the entire environment, given the required locomotion without the need for additional actuators for the sensors.
This requires a solution for the spherical simultaneous localization and mapping (SLAM) problem given the six degrees of freedom of the robot.
Secondly a spherical shell, that encloses all sensors protects these from possible hazardous environments.
For example, any dust that deteriorates sensors or actuators when settling at sensitive locations is stopped by a shell.
This is be particularly useful for unknown and dangerous environments.
E.g., for space applications this is also proposed in the DAEDALUS study~\cite{RossiMaurelliUnnithanetal.2021}, a spherical robot that is to be lowered into a lunar cave and create a 3D map of the environment. The authors choose this format as the present moon regolith is known to damage instruments and other components.
